A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-17 paper/theor-experiment.tex
making small edits from Andreas

For validation purposes we compared the results of the envelope-tracker using
  the analytical space charge model with the \textsc{OPAL} 3D macro particle
  tracker.
The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
  MeV injector.
The results for both rms beam size and emittance are shown in
  Figure~\ref{fig:et-vs-tt}.
A good agreement between the two codes can be observed.
The difference of the larger emittance along the solenoids in case of 3D
  tracker that is not seen by the envelope-tracker is due to the different
  definition of the particle momenta (canonical vs.~mechanical).
Both trackers agree within acceptable limits \cite{chao:99}.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are weighted 
equally and calculated at 
$s_3=19.4$~[m], see Fig.~\ref{awa-tba}. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

@@

With the time steps and hyper parameters set by the work in \ref{awa:subsection:test}, 
the full optimization problem described in \ref{awaproblem} was run for 200 generations.
The initial number of individuals was fixed at 656, 
and the minimum number individuals in later generations was fixed at 328. 
These numbers were in part based on the architecture of the KNL's. 
Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources.

>>>>

For validation purposes we compared the results of the envelope-tracker using
  the analytical space charge model with the \textsc{OPAL-T} 3D macro particle
  tracker.
The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
  MeV injector.
The results for both rms beam size and emittance are shown in
  Figure~\ref{fig:et-vs-tt}.
A good agreement between the two codes can be observed.
The difference of the larger emittance along the solenoids in case of 3D
  tracker that is not seen by the envelope-tracker is due to the different
  definition of the particle momenta (canonical vs.~mechanical).
Both trackers agree within acceptable limits \cite{chao:99}.

@@

\subsubsection{TBA Optimization Problem}
With computational and hyper parameters set, 
the full optimization problem of interest is explored.
The objectives (beam sizes and energy spread) are weighted 
equally and calculated at 
$s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
beam line elements. 
Given the longitudinal location of $s_3$ (unless otherwise noted), 
we define the objectives and input parameters as:
\begin{align}
\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
\end{align}

@@

With the time steps and hyper parameters set by the work in Section \ref{awa:subsection:test}, 
the full optimization problem described in \ref{awaproblem} was run for 200 generations.
The initial number of individuals was fixed at 656, 
and the minimum number individuals in later generations was fixed at 328. 
These numbers were in part based on the architecture of the KNL's. 
Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
we wanted a large population size that would fit evenly on these resources.
